Argennon: A Scalable Smart Contract Platform

### 2021-06-09 tex/sections/avm.tex
Fix a few typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The execution of smart contracts code in the AVM is done in execution sessions. Every execution session in the
Argennon Virtual Machine consists of a single method invocation from the \emph{root} smart contract and a list
of resource allocation requests. These allocation requests always include a request for allocating some amount
of execution time and a request for accessing some memory locations for reading or writing. If after the start
an execution session tries to violate its allocated resources, an \textbf{uncatchable} exception will
be thrown by the AVM\@.

@@

The root smart contract with the \texttt{applicationID} of zero, is a special smart contract in the Argennon
Virtual Machine. Its code is immutable and is a part of the AVM implementation. The root smart contract is always
run in the privileged mode, and every execution session starts with a call to a method of the root smart contract.
This method always transfers some amount of fee from an account ot the \texttt{feeSink} account and then it
performs the requested operation.

\note{Argennon transactions do not have a sender, and the payer of the transaction fee could be any
account who has provided the required digital signature.}

If the requested operation is a method invocation, the root smart contract will call the \texttt{Heap.Save()}
function once, and then it will invoke the requested method using \texttt{spawn} instruction. This means that the
invoked method will have a separate call stack and if it completes abruptly the changes made by the root
smart contract to the state will not be reverted.

>>>>

The execution of smart contracts code by the Argennon Virtual Machine is performed in execution sessions. Every
execution session consists of a single method invocation from the \emph{root} smart contract and a list
of resource allocation requests. These allocation requests always include a request for allocating some amount
of execution time and a request for accessing some memory locations for reading or writing. If after starting,
an execution session tries to violate its allocated resources, an \textbf{uncatchable} exception will
be thrown by the AVM\@.

@@

The root smart contract with the \texttt{applicationID} of zero, is a special smart contract in the Argennon
Virtual Machine. Its code is mutable and is a part of the Argennon protocol. The root smart contract is always
run in the privileged mode, and every Argennon transaction starts with a call to a method of the root smart contract.
This method always transfers some amount of fee from an account to the \texttt{feeSink} accounts and then it
performs the requested operation.

If the requested operation is a method invocation, the root smart contract will call the \texttt{Heap.Save()}
function, and then it will invoke the requested method using \texttt{spawn} instruction. This implies that the
invoked method will always have a separate call stack, and if it completes abruptly the changes made by the root
smart contract to the AVM state will not be reverted.

\note{Argennon transactions do not have a sender, and the payer of the transaction fee could be any
account who has provided the required digital signature for fee payment.}
